---
title: "p8105_hw1_wl2829"
author: "Wentong"
date: "9/26/2021"
output: github_document
---

```{r include=FALSE,echo=FALSE}
library(tidyverse)
```

## Problem 1

### Create dataframe
```{r}
problem1_df <- tibble(
  vec_random = rnorm(10, mean = 0, sd = 1),
  vec_logic = vec_random > 0,
  vec_char = c("This","is","Wentong","Liu's","answer","for","homework","1","problem","1"),
  vec_factor = factor(c("good","good","good","medium","medium","medium","medium","bad","bad","bad"))
)
```

### Take the mean of a variable in a dataframe
```{r}
mean(pull(problem1_df,vec_random))        # mean works
mean(pull(problem1_df,vec_logic))         # mean works
mean(pull(problem1_df,vec_char))          # mean does not work
mean(pull(problem1_df,vec_factor))        # mean does not work
```

### Convert variables
```{r eval=FALSE}
as.numeric(pull(problem1_df,vec_logic))   # "TRUE"and"FALSE" -> "0"and"1"
as.numeric(pull(problem1_df,vec_char))    # cannot be converted to numbers
as.numeric(pull(problem1_df,vec_factor))  # "good","medium","bad" -> "2","3","1"
```
Conclusion: The logic and factor can be converted. The mean of the logic vector works and it represents the tendency of true or false. On the other hand, the mean of factor vector can not be calculated because it is meaningless to some extent.

## Problem 2

### Data description

### The data of the "Penguins" is
```{r}
data ("penguins", package = "palmerpenguins")
force (penguins)                                               # data
mean (pull(penguins,flipper_length_mm), na.rm = TRUE)       # mean of flipper length  
```
At the mean time, "Penguins" dataset includes `r nrow(penguins)` subjects and `r ncol(penguins)` variables. The flipper length includes "NA", so we need to use "na.rm =TRUE" to calculate the rest numbers. The mean of the flipper length is `r mean ( pull ( penguins,flipper_length_mm ), na.rm = TRUE ) `. 

### Make a scatterplot
```{r}
# Use ggplot to create the plot
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = (species))) + geom_point()
# Use ggsave to save the plot
# ggsave("penguins_scatter_plot.pdf")
```



